% Canonical web-published CV source.
% Private address and phone information must never be added to this file.
% Build: pdflatex -jobname=Mantel_CV -output-directory=/tmp/pdfs cv/academic_resume.tex
\documentclass[11pt]{article}
\usepackage[top=0.75in,bottom=0.75in,left=1in,right=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{titlesec}
\usepackage{url}

\titlespacing{\section}{0pt}{12pt}{6pt}
\titleformat{\section}{\large\bfseries\scshape}{}{0pt}{}[\titlerule]
\pagestyle{empty}

\begin{document}

\begin{center}
  {\LARGE\bfseries Preston Mantel}\\[4pt]
  Ph.D. Candidate, Department of Finance\\
  Lindner College of Business, University of Cincinnati\\[3pt]
  \href{mailto:mantelpl@mail.uc.edu}{mantelpl@mail.uc.edu} \quad$\cdot$\quad
  \href{https://prestonmantel.com}{prestonmantel.com}
\end{center}

\section*{Education}

\noindent\textbf{Ph.D. in Finance}, University of Cincinnati \hfill 2022--Present \\
Dissertation: \textit{Essays on Market Microstructure Frictions and Retail Investors} \\
Committee: Mehmet Saglam (Chair) \\
GPA: 3.98/4.0

\vspace{6pt}
\noindent\textbf{B.S. in Mechanical Engineering}, Purdue University \hfill 2014--2018 \\
Minors: Computer Science, Global Engineering Studies \\
GPA: 3.7/4.0 \\
Study Abroad: Universidad Carlos III de Madrid, Spain \hfill Spring 2017

\section*{Research Interests}

\noindent Market Microstructure, Retail Investor Protection, Regulation, Price Discovery, Market Quality

\section*{Honors and Awards}

\noindent\textbf{Research Excellence Award}, Department of Finance, University of Cincinnati \hfill 2025

\vspace{4pt}
\noindent\textbf{Teaching Excellence Award}, Department of Finance, University of Cincinnati \hfill 2025

\section*{Working Papers}

\noindent Mantel, Preston. ``Taker Delays and Liquidity Provision in Prediction Markets.'' Working Paper, May 2026.

\vspace{6pt}
\noindent Mantel, Preston. ``When Lots Matter: The Impact of SEC Round Lot Modernization on Liquidity.'' Job Market Paper, November 2025. Available at SSRN: \url{https://ssrn.com/abstract=5757242}

\vspace{6pt}
\noindent Mantel, Preston and Mehmet Saglam. ``Democratizing or Demoralizing: The Impact of Robinhood's Order Types on Retail Trading Costs.'' Working Paper, November 2025. Available at SSRN: \url{https://ssrn.com/abstract=4377192}

\vspace{6pt}
\noindent Mantel, Preston and Mehmet Saglam. ``Discriminatory Market Making: Evidence from Institutional Trades.'' Working Paper, July 2026.

\vspace{6pt}
\noindent Mantel, Preston, Mehmet Saglam, and Tugkan Tuzun (Federal Reserve). ``Actively Traded ETFs.'' Working Paper, June 2025.

\section*{Papers Under Review}

\noindent ``Democratizing or Demoralizing: The Impact of Robinhood's Order Types on Retail Trading Costs'' \\
\indent Submitted to the \textit{Journal of Financial Economics}

\begin{samepage}
\section*{Conference Presentations}

\noindent ``Democratizing or Demoralizing: The Impact of Robinhood's Order Types on Retail Trading Costs''
\begin{itemize}[nosep, topsep=2pt, leftmargin=1.5em]
  \item Financial Management Association Annual Meeting, Chicago, IL \hfill 2023
  \item The Microstructure Exchange, Stockholm, Sweden \hfill 2023
  \item Southern Finance Association Annual Meeting \hfill 2024
\end{itemize}
\end{samepage}

\section*{Teaching Experience}

\noindent\textbf{Instructor of Record}, University of Cincinnati \hfill 2022--Present

\vspace{4pt}
\noindent\begin{tabular}{@{} l l l c | c c @{}}
\textbf{Course Title} & \textbf{Number} & \textbf{Semester} & \textbf{Students} & \multicolumn{2}{c}{\textbf{Evaluations}*} \\
 & & & & Mean & Median \\[2pt]
\hline
Financial Markets \& Institutions & FIN 4053 & Fall 2023 & 69 & 7.11 & 8 \\
Financial Modelling & FIN 4041 & Spring 2025 & 49 & 7.36 & 8 \\
Financial Modelling & FIN 4041 & Summer 2025 & 64 & 7.61 & 8 \\
\end{tabular}

\vspace{2pt}
{\small \textit{Evaluations reflect the ``instructor was excellent'' metric on an 8-point scale.}}

\vspace{6pt}
\noindent\textbf{Graduate Assistant}, University of Cincinnati \hfill 2022--2023

\section*{Service and Mentorship}

\begin{itemize}[nosep, topsep=2pt, leftmargin=1.5em]
  \item Advisor, Bloomberg Trading Competition student team, University of Cincinnati
\end{itemize}

\section*{Relevant Coursework}

\noindent Empirical and Theoretical Corporate Finance and Asset Pricing, Bayesian and Frequentist Econometrics, Advanced Microeconomics, Big Data Analytics, Game Theory, Statistical Modelling, Forecasting

\section*{Professional Experience}

\noindent\textbf{Founder \& COO}, Digital Paradise, Indianapolis, IN \hfill Aug. 2020--Aug. 2022\\
Founded marketing business; grew operations to over \$100K in yearly revenue with 2+ employees.

\vspace{6pt}
\noindent\textbf{Technology Consulting Analyst}, Deloitte, Chicago, IL \hfill Aug. 2019--Aug. 2020\\
Clients: Nestle and Intel.

\vspace{6pt}
\noindent\textbf{Director of Operations}, Watchtower Robotics, Boston, MA \hfill Jan. 2019--Jun. 2019\\
Managed 15 employees and \$175K in grant income.

\section*{Technical Skills}

\noindent\textbf{Programming:} Python, R, SQL, C, Java, HTML/CSS, MATLAB \\
\textbf{Software:} JMP, Catia, Microsoft Office, Adobe Creative Suite, \LaTeX

\end{document}
