% Web-published CV — mirrors archive/annual-reports/2026/preston_mantel_cv.pdf
% with home address and phone REMOVED (docs/content-rules.md) and website added.
% Build: pdflatex -output-directory=cv cv/Mantel_CV.tex ; copy PDF to static/files/
\documentclass[11pt]{article}
\usepackage[margin=0.8in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{parskip}
\pagestyle{empty}

\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{10pt}{4pt}
\setlength{\parskip}{4pt}
\newcommand{\entry}[2]{\noindent\textbf{#1}\hfill #2\par}
\setlist[itemize]{leftmargin=1.4em, topsep=2pt, itemsep=1pt, parsep=0pt}

\begin{document}

\begin{center}
  {\LARGE\bfseries Preston Mantel}\\[4pt]
  Ph.D. Candidate, Department of Finance\\
  Lindner College of Business, University of Cincinnati\\[3pt]
  \href{mailto:mantelpl@mail.uc.edu}{mantelpl@mail.uc.edu} \quad$\cdot$\quad
  \href{https://prestonmantel.com}{prestonmantel.com}
\end{center}

\section{Education}
\entry{Ph.D. in Finance, University of Cincinnati}{2022--Present}
Dissertation: \textit{Essays on Market Microstructure Frictions and Retail Investors}\\
Committee: Mehmet Saglam (Chair)\\
GPA: 3.98/4.0

\entry{B.S. in Mechanical Engineering, Purdue University}{2014--2018}
Minors: Computer Science, Global Engineering Studies\\
GPA: 3.7/4.0\\
Study Abroad: Universidad Carlos III de Madrid, Spain \hfill Spring 2017

\section{Research Interests}
Market Microstructure, Retail Investor Protection, Regulation, Price Discovery, Market Quality

\section{Honors and Awards}
\entry{Research Excellence Award, Department of Finance, University of Cincinnati}{2025}
\entry{Teaching Excellence Award, Department of Finance, University of Cincinnati}{2025}

\section{Working Papers}
Mantel, Preston. ``Taker Delays and Liquidity Provision in Prediction Markets.'' Working Paper, May 2026.
\begin{itemize}
  \item Studies how taker delays protect resting orders in short-duration prediction markets.
  \item Synchronizes Polymarket order books with Binance data and on-chain settlement records.
  \item Finds broader maker participation without a measurable loss in forecast accuracy.
\end{itemize}

Mantel, Preston. ``When Lots Matter: The Impact of SEC Round Lot Modernization on Liquidity.'' Working Paper, November 2025. Available at SSRN: \url{https://ssrn.com/abstract=5757242}
\begin{itemize}
  \item Examines how SEC round lot modernization changes displayed and realized trading costs.
  \item Separates the visibility, crumbling-quote, and adverse-selection channels behind the reform.
  \item Documents a large gap between headline spread improvements and savings realized by investors.
\end{itemize}

Mantel, Preston and Mehmet Saglam. ``Democratizing or Demoralizing: The Impact of Robinhood's Order Types on Retail Trading Costs.'' Working Paper, November 2025. Available at SSRN: \url{https://ssrn.com/abstract=4377192}
\begin{itemize}
  \item Studies how Robinhood's order-collaring policy affects retail execution costs.
  \item Combines regular-hours, after-hours, and SEC Rule 605 evidence.
  \item Identifies the broker incentives and investor costs created by the policy.
\end{itemize}

Mantel, Preston and Mehmet Saglam. ``Discriminatory Market Making: Evidence from Institutional Trades.'' Working Paper, July 2026.
\begin{itemize}
  \item Tests whether market makers price institutional clients according to inferred informativeness.
  \item Finds no broad discrimination against informed clients across execution-quality measures.
  \item Documents bilateral learning from a market maker's own profit-and-loss history with each client.
\end{itemize}

\begin{samepage}
Mantel, Preston, Mehmet Saglam, and Tugkan Tuzun (Federal Reserve). ``Actively Traded ETFs.'' Working Paper, June 2025.
\begin{itemize}
  \item Examines conflicts between managers and investors using trades from actively traded ETFs.
  \item Shows ETF trades predict abnormal volume and associates buy trades with positive one-day returns.
  \item Uses short-sale activity to study whether short sellers respond to ETF-driven mispricing.
\end{itemize}
\end{samepage}

\section{Papers Under Review}
``Democratizing or Demoralizing: The Impact of Robinhood's Order Types on Retail Trading Costs''\\
\hspace*{1.4em}Submitted to the \textit{Journal of Financial Economics}

\section{Conference Presentations}
``Democratizing or Demoralizing: The Impact of Robinhood's Order Types on Retail Trading Costs''
\begin{itemize}
  \item Financial Management Association Annual Meeting, Chicago, IL \hfill 2023
  \item The Microstructure Exchange, Stockholm, Sweden \hfill 2023
  \item Southern Finance Association Annual Meeting \hfill 2024
\end{itemize}

\section{Teaching Experience}
\entry{Instructor of Record, University of Cincinnati}{2022--Present}
\begin{itemize}
  \item Financial Markets \& Institutions (FIN 4053, 69 students) \hfill Fall 2023\\
        Evaluation (instructor was excellent): Mean 7.11, Median 8
  \item Financial Modelling (FIN 4041, 49 students) \hfill Spring 2025\\
        Evaluation (instructor was excellent): Mean 7.36, Median 8
  \item Financial Modelling (FIN 4041, 64 students) \hfill Summer 2025\\
        Evaluation (instructor was excellent): Mean 7.61, Median 8
\end{itemize}
\entry{Graduate Assistant, University of Cincinnati}{2022--2023}
\begin{itemize}
  \item Assisted with two finance courses
\end{itemize}

\section{Service and Mentorship}
\begin{itemize}
  \item Advisor, Bloomberg Trading Competition student team, University of Cincinnati
\end{itemize}

\section{Relevant Coursework}
Empirical and Theoretical Corporate Finance and Asset Pricing, Bayesian and Frequentist Econometrics, Advanced Microeconomics, Big Data Analytics, Game Theory, Statistical Modelling, Forecasting

\section{Professional Experience}
\entry{Founder \& COO, Digital Paradise, Indianapolis, IN}{Aug.\ 2020--Aug.\ 2022}
Founded marketing business; grew operations to over \$100K in yearly revenue with 2+ employees.

\entry{Technology Consulting Analyst, Deloitte, Chicago, IL}{Aug.\ 2019--Aug.\ 2020}
Clients: Nestle and Intel.

\entry{Director of Operations, Watchtower Robotics, Boston, MA}{Jan.\ 2019--Jun.\ 2019}
Managed 15 employees and \$175K in grant income.

\section{Technical Skills}
\textbf{Programming:} Python, R, SQL, C, Java, HTML/CSS, MATLAB\\
\textbf{Software:} JMP, Catia, Microsoft Office, Adobe Creative Suite, \LaTeX

\end{document}
